---
title: ""
output: bookdown::pdf_document2
classoption: 12pt
header-includes: 
  - \usepackage{"company-styles"}
  - \usepackage{"caption-styles"}
tidy: styler
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE,
	fig.pos = "h",
	out.extra = ""
)
```

# Gapminder

The `gapminder` package contains an excerpt of demographic data from the [Gapminder Foundation](http://www.gapminder.org/data/). 

```{r}
library("tidyverse")
library("gapminder")
```

The dataset includes the following variables for the years `r paste(gapminder$year %>% unique(), collapse = ", ")`:

- Life expectancy
- GDP per capita
- Population by country

There are `r length(unique(gapminder$country))` countries in the datset, Table \@ref(tab:countries-per-continent) summarises the number of countries per continent.

```{r countries-per-continent, fig.height=2}
library("kableExtra")
gapminder %>%
  select(continent, country) %>%
  unique() %>%
  count(continent) %>%
  knitr::kable(caption = "Countries per continent in the gapminder dataset") %>%
  kable_styling(latex_options = "hold_position")
```

## Continental populations

Figure \@ref(fig:mean-continent-population-2007) shows the mean population of each continent in 2007.

```{r mean-continent-population-2007, fig.cap="Continental mean population in 2007", fig.height=2}

gapminder %>%
  filter(year == max(year)) %>%
  group_by(continent) %>%
  summarise(mean_pop = mean(pop)) %>%
  ggplot(aes(x = fct_reorder(continent, mean_pop),
             y = mean_pop)) +
  geom_col() +
  coord_flip()
```

