---
title: "Recipes Analysis"
output: 
  html_document:
    df_print: kable
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
```


```{r data-processing, echo = FALSE}
library("tidyverse")
recipes_data_dir <- tempdir()
s2_zip <- tempfile(fileext = ".zip")
s3_zip <- tempfile(fileext = ".zip")

download.file(url = "https://media.nature.com/original/nature-assets/srep/2011/111215/srep00196/extref/srep00196-s2.zip", destfile = s2_zip)
download.file(url = "https://media.nature.com/original/nature-assets/srep/2011/111215/srep00196/extref/srep00196-s3.zip", destfile = s3_zip)

unzip(s2_zip, exdir = recipes_data_dir)
unzip(s3_zip, exdir = recipes_data_dir)

recipe_lists <-
  readLines(file.path(recipes_data_dir, "srep00196-s3.csv")) %>%
  strsplit(",")
recipe_lists <- recipe_lists[5:length(recipe_lists)]
recipes <- tibble(
  cuisine = map_chr(recipe_lists, 1),
  ingredients = map(recipe_lists, tail, -1)
) %>%
  rowwise() %>%
  mutate(n_ingredients = length(ingredients)) %>%
  ungroup()

shared_chemicals <-
  read_csv(
    file.path(recipes_data_dir, "srep00196-s2.csv"),
    skip = 4,
    col_names = c("ingredient.1", "ingredient.2", "shared.chemicals")
  )
```

Recipes are fascinating, there's huge variation in how different regional cuisines pair and prepare ingredients. In 2011 a huge collection of `r nrow(recipes)` were collated and analysed by academics in a free to read paper titled [Flavor network and the principles of food pairing](https://doi.org/10.1038/srep00196).

This report highlights some of the interesting features of the recipes.

## Ingredients across recipes

Here are the top 5 most used ingredients across all recipes:

```{r recipes-analysis-1}
ingredient_frequency <- recipes %>%
  select(ingredients) %>%
  unnest() %>%
  add_count(ingredients) %>%
  unique() %>%
  arrange(desc(n))

ingredient_frequency %>%
  head(n = 5)
```

```{r recipes-analysis-2}
single_use_ingredients <- ingredient_frequency %>%
  filter(n == 1)
```

There were only `r nrow(single_use_ingredients)` ingredients that appear in only one recipe:

```{r recipes-analysis-3}
single_use_ingredients %>%
  arrange(ingredients) %>%
  select(ingredients) %>%
  .[[1]]
```

## Recipe complexity by regional cuisine

One measure of the complexity of a recipe is the number of ingredients it contains. The chart below shows the median number of ingredients per recipe broken down by regional cuisine:

```{r median-ingredients-lollipop}
recipes %>%
  select(cuisine, n_ingredients) %>%
  group_by(cuisine) %>%
  summarise(median_ingredients = median(n_ingredients)) %>%
  mutate(
    cuisine = gsub("([[:upper:]])", " \\1", cuisine),
    cuisine = trimws(cuisine)
  ) %>%
  ggplot(aes(
    x = fct_reorder(cuisine, median_ingredients),
    y = median_ingredients
  )) +
  scale_y_continuous(
    breaks = 0:11,
    limits = c(0, 11.5),
    expand = c(0, 0)
  ) +
  geom_segment(aes(xend = cuisine, y = 0, yend = median_ingredients),
    colour = "#4286f4"
  ) +
  geom_point(
    size = 5,
    colour = "#4286f4"
  ) +
  labs(
    x = "Regional cuisine", y = "Median number of ingredients per recipe",
    title = "Average number of ingredients per recipe in different regional cuisines"
  ) +
  coord_flip() +
  theme_bw() +
  theme(axis.ticks.y = element_blank()) +
  NULL
```




