---
title: "Beamer features"
output: 
  beamer_presentation:
    includes:
      in_header: styles/header_pagenrs.tex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Where did beamer come from?

The `beamer_presentation` format comes from the extremely popular beamer LaTeX class, which is used widely in academia.

- [Github repository for Beamer](https://github.com/josephwright/beamer)

## Benefits of using beamer

The `beamer_presentation` format has a number of useful features:

- Default fonts and styles are designed for readability, helping to reduce information overload per slide.

## Disadvantages of using beamer

Beamer defaults do not include slide numbers or any other information about the slide deck.

You must write \LaTeX in order to insert page numbers.

## Inserting slide numbers

This .Rmd has been customised to include slide numbers in the footer by following two steps:

1. Add this to your YAML header:

        output: 
          beamer_presentation:
            includes:
              in_header: styles/header_pagenrs.tex

1. Create a new file `styles/header_pagenrs.tex` and add these two lines:

```{r, eval = FALSE}
\setbeamertemplate{navigation symbols}{}
\setbeamertemplate{footline}[page number]
```

## Use these slides as a template!

Consider using this .Rmd file as your template for presentation presentations as it contains all of the features I've explained and a bit more.