---
title: "Untitled"
output: pdf_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE,
	out.extra = "",
	fig.pos = "h"
)
```

# Raw \LaTeX

\LaTeX  can be inserted into RMarkdown documents without issue

\begin{equation} 
  f\left(k\right) = \binom{n}{k} p^k\left(1-p\right)^{n-k}
\end{equation}

# Escaping LaTeX symbols

Most \LaTeX special characters do not need to be escaped in prose, the only ones that do are:

- \# (written as \\#)
- \\ (written as \\\\)

So, the following can be used verbatim: $, %, &, ~, _, ^,
{, }.

However, they must be double escaped within code chunks. For instance, in the caption for Fig.\@ref(fig:mean-gdp-chart) the $ symbol is written as \\\\$

```{r mean-gdp-chart, fig.cap="Mean GDP per employeed person (2010-2015, 2011 \\$)", fig.height=2}
library("gapminder")
library("tidyverse")
library("WDI")
library("scales")

countries <- c("EE", "EG", "SG", "CN", "EC", "PG")

gdp_per_employee <- WDI(
  country = countries, indicator = "SL.GDP.PCAP.EM.KD",
  start = 2010, end = 2015
)

gdp_per_employee %>%
  group_by(country) %>%
  summarise(mean_gdp = mean(SL.GDP.PCAP.EM.KD)) %>%
  mutate(country = fct_reorder(country, mean_gdp)) %>%
  ggplot(aes(x = country, y = mean_gdp)) +
  geom_col() +
  scale_y_continuous(labels = dollar) +
  labs(x = "", y = "Mean GDP per employeed person") +
  coord_flip()
```



