---
title: "Movie profitability and the Bechdel test"
output: 
  html_document:
    df_print: paged
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
```
```{r}
head(iris)
```




Some folks in Hollywood claim that movies with female characters make less in the box office, [FiveThirtyEight showed us that's not the case](https://fivethirtyeight.com/features/the-dollar-and-cents-case-against-hollywoods-exclusion-of-women/). The `fivethirtyeight` package includes the dataset behind this analysis, and many more.

Let's take a look at the top 20 highest grossing films published after 1990, 80% of the films pass the Bechdel test[^1].

```{r}
library("tidyverse")
library("fivethirtyeight")
bechdel %>%
  filter(year > 1990) %>%
  select(title, year, clean_test, binary, intgross_2013) %>%
  arrange(desc(intgross_2013)) %>%
  slice(1:20)
```

When comparing the profitability of films, films that pass the Bechdel have a higher median profitability than any other category!

```{r}
bechdel %>%
  # filter(year > 1990) %>%
  mutate(profitability = intgross_2013 / budget_2013) %>%
  group_by(clean_test) %>%
  summarise(median_profitability = median(profitability, na.rm = TRUE)) %>%
  arrange(desc(median_profitability))
```

Boxplots provide more information that the summary statitics in the table above are able to communicate.

```{r}
bechdel %>%
  filter(year > 1990) %>%
  mutate(profitability = intgross_2013 / budget_2013) %>%
  filter(profitability < 50) %>%
  group_by(clean_test) %>%
  ggplot(aes(x = clean_test,
             y = profitability)) +
  geom_boxplot() +
  coord_flip() +
  theme_bw()
```

[^1]: Read more about the Bechdel Test on [bechdeltest.com](https://bechdeltest.com/).